Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-09 writeup/gz_hubble_data.tex

\begin{figure}
\center
\includegraphics[width=0.5\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
includes only galaxies with a bounded range on the dropoff
\changes{($-10<\zeta<10$)} and sufficient points to fit each function (37~original
galaxies, each artificially redshifted in eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$).}
\label{fig:zeta_mu}
\end{figure}

>>>>

\begin{figure}
\center
\includegraphics[width=0.5\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
includes only the simulated galaxies with a bounded range on the dropoff
\changes{($-10<\zeta<10$)} and sufficient points to fit each function (\changes{28~original
galaxies, each with varying images artificially redshifted in one to eight bins over a range from} $0.3\lesssim z_\mathrm{sim}\lesssim1.0$). 
}
\label{fig:zeta_mu}
\end{figure}
